Practical Optional Types for Clojure

### 2015-02-28 conclusion.tex
Related work.
missing cites.

However, there is much more that Typed Clojure can provide. Most
significantly, Typed Clojure currently does not provide \emph{gradual
  typing}---ineraction between typed and untyped code is unchecked and
thus unsound. We hope to explore the possibilites of using existing
mechanisms for contracts and proxies in Java and
Clojure~\cite{some-stuff} to enable sound gradual typing for Clojure.

@@

Finally, our case study and broader experience indicate that Clojure
programmers still find themselves unable to use Typed Clojure on some
of their programs for lack of expressiveness. This requires continued
effort to analyze and understand the relevant features and idioms and
develop new type checking approaches for them.

>>>>

% Delete the following paragraphs if space is needed.

However, there is much more that Typed Clojure can provide. Most
significantly, Typed Clojure currently does not provide \emph{gradual
  typing}---ineraction between typed and untyped code is unchecked and
thus unsound. We hope to explore the possibilites of using existing
mechanisms for contracts and proxies in Java and
Clojure to enable sound gradual typing for Clojure.

@@

Finally, our case study and broader experience indicate that Clojure
programmers still find themselves unable to use Typed Clojure on some
of their programs for lack of expressiveness. This requires continued
effort to analyze and understand the relevant features and idioms and
develop new type checking approaches.
